---
title: "Use Custom `end`- and `login` - Functions to Controll Access"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use Custom `end`- and `login` - Functions to Controll Access}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
 
This example shows how to use the package `ShinyItemBuilder` with a custom `end`- and `login`-functions, to implement different approaches for authentication. We will use the items provided as `demo01`.

### The Start of an Assessment

#### Anonymous Access

By default, `ShinyItemBuilder` is configured to give access to anyone that knows the URL.

```{r login_configuration_01, eval=FALSE}
library(ShinyItemBuilder)

item_pool <- getDemoPool("demo01")
assessment_config <- getConfig()
shinyApp(assessmentOutput(pool = item_pool, config = assessment_config,overwrite=T),
         renderAssessment)
```


#### Login Dialog

Using the option `sessiontype="provided"`, this behavior can be changed. 

```{r login_configuration_02, eval=FALSE}
library(ShinyItemBuilder)

item_pool <- getDemoPool("demo01")
assessment_config <- getConfig(sessiontype="provided")

assessment_config$login=function(session){
  showModal(modalDialog(
    tags$h2('Login'),
    tags$div('Please enter a valid token and press "OK".'),
    textInput('queryStringParameter', ''),
    footer=tagList(
      actionButton('submitLoginOK', 'OK')
    )
  ))
}

assessment_config$custom_list_accounts <- sprintf("%03d", 0:99)

assessment_config$validate=function(token_or_login=NULL, password=NULL, config){
  if (is.null(token_or_login)||length(token_or_login)==0)
  {
    return (FALSE)
  }
  else {
    if (!is.na(match(token_or_login,config$custom_list_accounts))){
      return (TRUE)
    }
  }
  FALSE
}
   
shinyApp(assessmentOutput(pool = item_pool, config = assessment_config,overwrite=T),
         renderAssessment)
```


### The End of an Assessment

#### Multiple Runs

To allow multiple runs, the `end`-function needs to contain an `actionButton` with the name `endActionButtonOK`: 

```{r end_configuration_01, eval=FALSE}
assessment_config$end=function(session){
    showModal(modalDialog(
      title = "You Answered all Items",
      "Please close the browser / tab or click 'Restart'.",
      footer = tagList(actionButton("endActionButtonOK", "Restart"))))
  }
```

#### Single Runs (End-Page)

If the  `end`-function does not contain an `actionButton` with the name `endActionButtonOK`, the test-taker can not restart the assessment, as long as the session is stored in the browser. 

```{r end_configuration_02, eval=FALSE}
assessment_config$end=function(session){
    showModal(modalDialog(
      title = "You Answered all Items",
      "Please close the browser / tab.",
      footer = tagList()))
  }
```


#### Single Runs (Redirect)

```{r end_configuration_03, eval=FALSE}
assessment_config$end=function(session){
  session$sendCustomMessage("shinyassess_redirect", 
      "https://URL-TO-REDIRECT.SOMEWERE/?QUERYSTRING")
}
```
