---
title: "Use Custom `end`-Function to Provide Immediate Feedback using Knitr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use Custom `end`-Function to Provide Immediate Feedback using Knitr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This example shows how to use the package `ShinyItemBuilder` to display a feedback after an assessment. 

```{r setup}
library(ShinyItemBuilder)
```

For illustration purposes, three items from the `demo01` included in the package `ShinyItemBuilder` are used. After calling `getDemoPool("demo01")` the object `item_pool` contains information about all items, but we only select item 2, 3 and 4:

```{r default_item_pool, eval=F}
item_pool <- getDemoPool("demo01")
item_pool <- item_pool[c(2,3,4),]
```

```{r default_item_pool_print, eval=T, echo=F}
item_pool <- getDemoPool("demo01")
item_pool <- item_pool[c(2,3,4),]
knitr::kable(item_pool[,c("Project","Task")], format = "html",row.names = T,booktabs = T)
```
 
To implement the booklet design, we overwrite the end function. 

```{r default_configuration}
assessment_config <- getConfig(Verbose = T) 
```

After calling `getConfig()`, the object `assessment_config` already contains the (default) implementation of the `end`-function:

```{r default_navigation_print}
assessment_config$end
```
This function can be overwritten by assigning a new function `end = function(session)` with the same signature. In this new function, we first load the data gathered for this session, stored in the variable `session$userData$cbasession`:

```{r default_data, eval=F}
data <- runtime.data[[session$userData$cbasession]
```

In the following lines we create a simple data.frame representation of the scoring results:

```{r default_table, eval=F}
  a <- NULL
  for (d in 1:dim(data$ResultData)[1]){
    s <- parse_ib_scoring(data$ResultData[d,"Resultdata"])
    a <- rbind(a,cbind(Project=data$ResultData[d,"Project"],
                       Task=data$ResultData[d,"Task"],
                       Scope=data$ResultData[d,"Scope"],
                       s[s$Active,c("Name","ResultText")]))
  }
```

This is followed by the markdown template that will be used to generate the feedback. In this example the markdown is created within the function, but it could also be stored in a separate `*.Rmd` file. 

After writing the markdown template to file (see `write(template, ...)`), render it to html (see `rmarkdown::render(...)`), the generated content is loaded from file as base64 encoded string (see `base64enc::dataURI(file = ...)`). Finally, the generated html (as base64 encoded string) is displayed in a modal dialog:

```{r default_dialog, eval=F}
  showModal(modalDialog(
    title = "Feedback",
    footer = tagList(actionButton("endActionButtonOK", "Restart")),
    renderUI({
      tags$iframe(src=b64, height=400, width=550, frameBorder=0)
    }),
  ), session)
```

Taking everything together, this is an custom `end`-function that provides immediate feedback about the scores obtained in CBA ItemBuilder items:

```{r custom_end_function}
assessment_config$end <- function(session) {

  data <- runtime.data[[session$userData$cbasession]]
  a <- NULL
  for (d in 1:dim(data$ResultData)[1]){
    s <- parse_ib_scoring(data$ResultData[d,"Resultdata"])
    a <- rbind(a,cbind(Project=data$ResultData[d,"Project"],
                       Task=data$ResultData[d,"Task"],
                       Scope=data$ResultData[d,"Scope"],
                       s[s$Active,c("Name","ResultText")]))
  }
 
  template <- '---
    output: html_document
    ---
    ### Your Results: A Score of `r sum(a$Name == "ScoreCorrect")`

    ``` {r, echo=F}
    knitr::kable(a)
    ```
'
  write(template, file=paste0(session$userData$cbasession,".rmd"), append = FALSE)
  
  tmpfile <- rmarkdown::render(paste0(session$userData$cbasession,".rmd"))
  b64 <- base64enc::dataURI(file = tmpfile, mime = "text/html")

  if (file.exists(tmpfile))
    file.remove(tmpfile)

  if (file.exists(paste0(session$userData$cbasession,".rmd")))
    file.remove(paste0(session$userData$cbasession,".rmd"))

  showModal(modalDialog(
    title = "Feedback",
    footer = tagList(actionButton("endActionButtonOK", "Restart")),
    renderUI({
      tags$iframe(src=b64, height=400, width=550, frameBorder=0)
    }),
  ), session)
}
```

Note that the dialog includes the actionButton with the name `endActionButtonOK` (see `footer = tagList(actionButton("endActionButtonOK", "Restart"))`), that restarts the assessment. 
